A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
remove more columns

```{r classifyData}
PM_MB_dat <-
   PM_MB_dat %>%
   mutate(trial_ref = as.character(trial_ref)) %>%
   mutate(year = as.character(year)) %>%
   mutate(location = as.character(location)) %>%
   mutate(host_genotype = as.character(host_genotype)) %>%
   mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
   mutate(replicates = as.integer(replicates)) %>%
   mutate(planting_date = ymd(planting_date)) %>%
   mutate(flowering_date = ymd(flowering_date)) %>%
   mutate(pod_fill_date = ymd(pod_fill_date)) %>%
   mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
   mutate(first_sign_disease = ymd(first_sign_disease)) %>%
   mutate(fungicide_ai = as.character(fungicide_ai)) %>%
   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2)) %>%
   mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
   mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
   mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
   mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
   mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
   mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
   mutate(total_fungicide = as.integer(total_fungicide)) %>%
   mutate(harvest_date = ymd(harvest_date)) %>%
   mutate(final_assessment = ymd(final_assessment)) %>%
   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4)) %>%
   mutate(disease_error = round(as.double(disease_error), digits = 6)) %>%
   mutate(D_error_type = as.character(D_error_type)) %>%
   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4)) %>%
   mutate(yield_error = round(as.double(yield_error), digits = 6)) %>%
   mutate(Y_error_type = as.character(Y_error_type)) %>%
   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6)) %>%
   mutate(yield_gain = round(as.double(yield_gain), digits = 4)) %>%
   mutate(prop_YG = round(as.double(prop_YG), digits = 4)) %>%
   select(
      -c(
         trial_design,
         # remove the following columns
         plot_length.m.,
         plot_width.m.,
         plant_density,
         trade_name,
         n_treatment,
         emergence_date,
         rating_scale,
         raw_graded,
         raw_data_avail,
         comments,
         days_harvest.planting,
         AUDPS_m,
         AUDPC_sd,
         Inc_Ms,
         pod_fill_date,
         mid_late_pod_fill,
         yield_gain,
         Y_Msquare,
         prop_YG,
         AUDPC_m,
         AUDPC_sd
      )
   )
```

>>>>

```{r classifyData}
PM_MB_dat <-
   PM_MB_dat %>%
   mutate(trial_ref = as.character(trial_ref)) %>%
   mutate(year = as.character(year)) %>%
   mutate(location = as.character(location)) %>%
   mutate(host_genotype = as.character(host_genotype)) %>%
   mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
   mutate(replicates = as.integer(replicates)) %>%
   mutate(planting_date = ymd(planting_date)) %>%
   mutate(flowering_date = ymd(flowering_date)) %>%
   mutate(pod_fill_date = ymd(pod_fill_date)) %>%
   mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
   mutate(first_sign_disease = ymd(first_sign_disease)) %>%
   mutate(fungicide_ai = as.character(fungicide_ai)) %>%
   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2)) %>%
   mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
   mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
   mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
   mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
   mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
   mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
   mutate(total_fungicide = as.integer(total_fungicide)) %>%
   mutate(harvest_date = ymd(harvest_date)) %>%
   mutate(final_assessment = ymd(final_assessment)) %>%
   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4)) %>%
   mutate(disease_error = round(as.double(disease_error), digits = 6)) %>%
   mutate(D_error_type = as.character(D_error_type)) %>%
   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4)) %>%
   mutate(yield_error = round(as.double(yield_error), digits = 6)) %>%
   mutate(Y_error_type = as.character(Y_error_type)) %>%
   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6)) %>%
   mutate(yield_gain = round(as.double(yield_gain), digits = 4)) %>%
   mutate(prop_YG = round(as.double(prop_YG), digits = 4)) %>%
   select(
      -c(
         trial_design,
         # remove the following columns
         plot_length.m.,
         plot_width.m.,
         plant_density,
         trade_name,
         n_treatment,
         emergence_date,
         rating_scale,
         raw_graded,
         raw_data_avail,
         comments,
         days_harvest.planting,
         AUDPS_m,
         AUDPC_sd,
         Inc_Ms,
         pod_fill_date,
         mid_late_pod_fill,
         flowering_date,
         yield_gain,
         Y_Msquare,
         prop_YG,
         AUDPC_m,
         AUDPC_sd,
         AUDPS_sd
      )
   )
```
